VM-Centric Deduplication with Fault Isolation for Snapshot Backup in the Cloud

### 2014-01-27 snapshot_system/paper_intro.tex
update intro to converged arch

One of emerging architectures for building cloud services
is a converged storage architecture that leverages commodity servers with software clustered storage.
The converged architecture (server plus compute in same tier) grew out of the Google model. What Google recognized is that they could leverage their software to meld multiple direct attached low-cost disks together across servers and avoid paying high margins for traditional network attached storage systems. %This(e.g. ~\cite{NutanixPaper}). 
Leading cloud platform companies such as Google, Amazon, Alibaba,
Microsoft Azure  have built a converged compute and storage infrastructure and used
a distributed file system such as Google file system~\cite{googlefs03,hdfs10}
to glue a large number of commodity servers.
% with local storage into a single cluster.
In such an environment,
%That  allows the use of scalable compute and storage, without incurring the costs and
%performance limitations associated with network storage.
each physical machine runs a number  of virtual machines 
%as  instances of a guest operating system 
and their  virtual disks are represented as virtual disk image files in the host operating system.
Frequent  snapshot backup of virtual disk images  can increase  the service reliability
and deduplication of redundant content blocks~\cite{venti02,bottleneck08}
 is necessary to substantially reduce the storage demand.
%For example, the Aliyun cloud, which is  the largest cloud service provider by Alibaba in China, 
%automatically conducts  the backup of virtual disk images to all active users every day.
%The cost of supporting a large number of concurrent backup streams is high
%because of the huge storage demand and the use of deduplication

>>>>

One of emerging architectures for building cloud services
is a converged storage architecture that leverages commodity servers with software clustered storage.
This converged architecture (server plus compute in same tier) grew out of the Google model. 
What Google recognized is that they could leverage their software to 
meld multiple direct attached low-cost disks together across servers, 
such approach allow Google to avoid paying high margins to traditional network attached storage vendors,
as well as ditching their scalability limitations.

Server virtualization is one of the most benefited area of adopting converged storage architecture.
Leading cloud platform providers such as Google AppEngine, Amazon AWS, 
Microsoft Azure and Alibaba have built such a converged compute and storage infrastructure and used
a distributed file system such as Google file system~\cite{googlefs03,hdfs10}
to glue a large number of commodity servers.
Many VDI environment in private clouds are also adopting this converged architecture 
provided by Nutanix~\cite{NutanixPaper}, Simplivity and others. 
% with local storage into a single cluster.
In such an environment,
%That  allows the use of scalable compute and storage, without incurring the costs and
%performance limitations associated with network storage.
each physical machine runs a number  of virtual machines 
%as  instances of a guest operating system 
and their virtual disks are represented as virtual disk image files in the host operating system.
Frequent snapshot backup of virtual disk images  can increase  the service reliability
and deduplication of redundant content blocks~\cite{venti02,bottleneck08}
 is necessary to substantially reduce the storage demand.
%For example, the Aliyun cloud, which is  the largest cloud service provider by Alibaba in China, 
%automatically conducts  the backup of virtual disk images to all active users every day.
%The cost of supporting a large number of concurrent backup streams is high
%because of the huge storage demand and the use of deduplication
